Distance distribution by modes

### 2019-08-07 code/trips_analysis/trip_distance.Rmd
select -> dplyr::select

rd1 <- io$accra$trip_scen_sets %>% mutate(cs = 'Accra') %>% select(cs, trip_distance, trip_distance_cat)
rd2 <- io$sao_paulo$trip_scen_sets %>% mutate(cs = 'Sao Paulo') %>% select(cs, trip_distance, trip_distance_cat)
rd3 <- io$delhi$trip_scen_sets %>% mutate(cs = 'Delhi') %>% select(cs, trip_distance, trip_distance_cat)

@@

  tl[[index]] <-  filter(p$data, scenario == 'Baseline') %>% select(trip_mode, trip_distance) %>% rename(var = trip_distance) %>% group_by(trip_mode) %>%  summarise(mean = mean(var), median =median(var), Q1 = quantile (var, probs=0.25), Q2 = quantile (var, probs=0.50), Q3 = quantile(var, probs=0.75)) %>% mutate_if(is.numeric, round, digits = 1)

>>>>

rd1 <- io$accra$trip_scen_sets %>% mutate(cs = 'Accra') %>% dplyr::select(cs, trip_distance, trip_distance_cat)
rd2 <- io$sao_paulo$trip_scen_sets %>% mutate(cs = 'Sao Paulo') %>% dplyr::select(cs, trip_distance, trip_distance_cat)
rd3 <- io$delhi$trip_scen_sets %>% mutate(cs = 'Delhi') %>% dplyr::select(cs, trip_distance, trip_distance_cat)

@@

  tl[[index]] <-  filter(p$data, scenario == 'Baseline') %>% dplyr::select(trip_mode, trip_distance) %>% rename(var = trip_distance) %>% group_by(trip_mode) %>%  summarise(mean = mean(var), median =median(var), Q1 = quantile (var, probs=0.25), Q2 = quantile (var, probs=0.50), Q3 = quantile(var, probs=0.75)) %>% mutate_if(is.numeric, round, digits = 1)
